\cvsection{Work Experience}
\begin{cventries}

  \cventry
   {Haskell}
   {ACA Project (Association of Computing Activities)}
  {Kanpur,India}
  {2016}
  {
    \begin{cvitems}
      \item Learned basic \textbf{functional programming} in \textbf{Haskell}.
      \item Made a two-player game of \textbf{NxN Tic-Tac-Toe} in Haskell.
      \item Implemented Taylor Series of Sine function to an error limit.
      \item Applied \textbf{Mini-Max Algorithm} to the game in Haskell.
    \end{cvitems}
  }

  \cventry
  {Line Following Robot}
  {Robotics Club, Winter Camp}
  {Kanpur, India}
  {Dec. 2016}
  {
    \begin{cvitems}
      \item Programmed the \textbf{Arduino} for functioning of robot.
      \item Implemented an \textbf{IR Sensor array} in a robot.
      \item Applied \textbf{PID algorithm} for traversal of robot.
      \item Integrated \textbf{maze solving algorithm} in the robot.
    \end{cvitems}
  }

  \cventry
  {Android App Development}
  {Google Dev-Fest}
  {Google}
  {2016}
  {
    \begin{cvitems}
    \item Developed an App to \textbf{digitize payement methods} on \textbf{Android Studio}.
    \item Generated a \textbf{QR code} based upon the data entered by the user.
    \item Used \textbf{Web-view} to display the QR-code fetched from internet.
    \item App also aimed at monitoring expenses by the user itself.
    \end{cvitems}
  }

  \cventry
  {Android App Development}
  {Code.Fun.Do}
  {Microsoft India}
  {2016}
  {
    \begin{cvitems}
    \item Developed a two-player logic based \textbf{Android Game} on \textbf{Android studio}.
    \item Generated a random grid amongst five random grid.
    \item Implemented \textbf{Dynamic Programming} to check for a valid path between two points.
    \end{cvitems}
  }
\end{cventries}
